Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
minor changes to paper

The first t seconds comes from the first coarse approximation, without which the parareal algorithm degenerates to $g_{\Delta t}$,  In order for there to be a speedup relative to the fine operator, we require
that $t + k(t + Qt/N) < Qt$, or $k < \frac{Q - 1}{1 + Q/N}$ or $N > \frac{Qk}{Q
- 1 - k}$. This can be tuned with by either adjusting the the quality factor or reducing the number of iterations, but the number of iterations, k, is important for error convergence to that of $g_{\textnormal{fine}}$.  However, this optimal k is a problem-specific parameter and must be optimized for.

>>>>

The first t seconds comes from the first coarse approximation, without which the parareal algorithm degenerates to $g_{\Delta t}$. In order for there to be a speedup relative to the fine operator, we require
that $t + k(t + Qt/N) < Qt$, or $k < \frac{Q - 1}{1 + Q/N}$ or $N > \frac{Qk}{Q
- 1 - k}$. This can be tuned with by either adjusting the the quality factor or reducing the number of iterations, but the number of iterations, k, is important for error convergence to that of $g_{\textnormal{fine}}$. However, this optimal k is a problem-specific parameter and must be optimized for.
